\subsection{GrConvNet}
% grasp height
As described in \ref{} we had to use a coarse approximation of the grasp height in order to generate grasp candidates for the \textit{GrConvNet} algorithm.
This approximation however is error prone to object with a non-planar surface.

% overfitting
Abother indicator that \textit{GrConvNet} might suffer from an overfitting problem is demonstrated in \ref{}.
For a plain

% small gripper width
A factor
We observed many cases were the grasp axis seemed to be generated with a proper orientation but the grasp center point was not placed correctly.
Especialy in cases where there is not much tolerance for the grasp center point due to the object size along the grasp axis limited maximum gripper.
It must be noted that this is an robot specific issue and might not occur for end effectors which offer a larger maximum gripper width.
However, in cluttered environements this can lead to a significant decrease in performance as a offseted grasp center point can lead to a collision
with other objects in the scene.

\subsection{ContactGraspNet}
In some cases the \textit{ContactGraspNet} algorithm wasn't able to generate any grasp candidates for a given object.
We assume that whic was caused by filtering executed in the \textit{ContactGraspNet} algorithm.
This means that underlying network was able to generate grasp candidates but they were filtered due to the applied constraints like collision avoidance
and object segmentation.


\subsection{GGCNN}
Similar to the \textit{GrConvNet} the \textit{GGCNN} algorithm also had problems in estimating the grasp height correctly.
In many of the observed cases the generated grasps

\subsection{Comparison}


In the previous section we described the different algorithms which were benchmarked.
The different approaches used by these algorithms lead to different strengths and weaknesses.
For a better undersanding of the results we will now discuss the limitations of the different algorithms and the differences between them.

The planar grasp algorith have the advantage that they are fast and can be used in real-time.
A major downside however is that the best, or in some cases the onyl possible grasp axis are not parallel to the image space.
Also it becomes increasingly challengin to obtain a suitable transformation for camera orientation which are not parallel to the surface the object is lying on.

The issues arising from the reduced orientation space of planar grasps are bypassed by approaches which use fully spatial grasp representations.
The unrestricted orientation space however also leads to a challenge in approaching the object without colliding with the object.
The analysed ContactGraspNet algorithm proposes no direct way of handling this issue.
However, as argued in \cite{} the algorithm used only points within the view area of the camera and therfore reducing the chance og generating grasp poses which will
lead to a collision whilc approachin the grasp position.



